%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[UTF8]{ctex}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}


\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Kevin Yipu Wu} % Your name
\address{kwu06@wm.edu \ \\ \  \href{ypwk.github.io}{ypwk.github.io}  \ \\ \ Williamsburg, VA}

\begin{document}

\begin{rSection}{EDUCATION}
    \begin{rSubsection} {William \& Mary}{Williamsburg, VA}{CS GPA: 3.88/4, GPA: 3.78/4}{August 2020 - May 2024}
        \startitems
        \item B.S. Computer Science and Mathematics Double Major
    \end{rSubsection}

    \begin{rSubsection}{Thomas Jefferson High School for Science and Technology}{Alexandria, VA}{GPA: 4.22/4}{August 2016 - May 2020} \end{rSubsection} 
\end{rSection}

\begin{rSection}{Publications}
    \item Chi-Kwong Li, \textbf{Kevin Y. Wu}, and Zherui Zhang. \textit{Efficient Circuit-Based Quantum State Tomography via Sparse Entry Optimization}. In preparation.  
\end{rSection}

\begin{rSection}{Experience}

    \begin{rSubsection}{Quantum Federated Learning} {Advisor: Qun Li}{November 2023 - Present}{William \& Mary}
        \startitems
        \item Trained a federated QCNN using the Qiskit Machine Learning library, achieving 89\% simulator test accuracy and 70\% IBM QPU test accuracy on the MNIST dataset.
        \item Implemented differential privacy to obfuscate sensitive client data, and performed a hyperparameter search to find an appropriate level of privacy.  
    \end{rSubsection}

    \begin{rSubsection}{\href{https://github.com/ypwk/DecoderVIS/tree/main}{DecoderVIS: Topological QECC Visualization}}{Self-directed}{March 2023 - April 2023}{{William \& Mary}}
        \startitems
        \item A topological quantum error correction code visualization written in C++. 
        \item Visualizer simulates a quantum memory experiment carried out on odd distance rotated planar codes, subject to i.i.d. depolarizing noise.
        \item Implemented minimum weight perfect matching decoding using the LEMON library. 
        \item Wrote a custom 2D rendering engine from scratch using GLFW and GLM to render the surface code, and created a minimal UI with Hello ImGUI.
    \end{rSubsection}

    \begin{rSubsection}{Quantum Operator Approximation}{Advisor: Chi-Kwong Li}{September 2022 - October 2022}{{William \& Mary}}
        \startitems
        \item Approximated arbitrary quantum operators using the Pauli product rotations, exponentiated elements of the Pauli group. 
        \item Transformed problem into nonconvex positive semidefinite programming problem, and optimized using a trust-region approach.
    \end{rSubsection}

    \begin{rSubsection}{First AI/ML Challenge at Dahlgren} {Advisor: Qun Li}{December 2022 - March 2023}{Naval Surface Warfare Center Dahlgren Division}
        \startitems
        \item Contributed to a white paper detailing relevant literature and proposed approaches on the weapon target assignment problem, which resulted in the team's acceptance to the competition.
        \item Played a leading role in brainstorming and implementing approaches for automatic scheduling and coordination of advanced weapon systems. 
        \item Architected, implemented, and trained several approaches to reduce damage to high value assets, including a Deep Q-Learning agent and heuristic-driven Greedy agent. 
        \item The W\&M team won 3rd place and \$20,000 in prize money. 
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Work Experience}  
    \begin{rSubsection}{Solutions Architect Intern}{Amazon Web Services}{September 2022 - August 2023}{Seattle, WA}
        \startitems
        \item Implemented an end-to-end quantum error mitigation scheme, based on \href{https://dl.acm.org/doi/abs/10.1145/3579371.3589043}{this result}. Used Poisson distributions fit on quantum processor metadata to predict and reduce quantum noise. Constructed a quantum circuit transpilation protocol in Python to aid in this endeavor. 
        \item Investigated relevant literature in cloud quantum computing, quantum error mitigation, and LLM retrieval augmented generation.
        \item Studied for and achieved the Cloud Practitioner and Associate Solutions Architect AWS Certifications.
        \item Completed mock customer conversations and shadowed customer calls.
    \end{rSubsection}

    \begin{rSubsection}{Junior Software Developer}{ESPX Global Inc.}{September 2021 - September 2022}{McLean, VA}
        \startitems
        \item Engineered a data lake solution capturing market conditions and features of the electric grid.
        \item Agilely collaborated remotely with a team of developers to create a minimum viable product conforming to client expectations.
        \item Selected, acquired, normalized, and analyzed data using Python, AWS services, and SQL.
        \item Managed and maintained the company website, along with related SSL certificate. 
    \end{rSubsection}

      \begin{rSubsection}{Student Intern Team Lead}{Asian Americans in Energy, Environment, and Commerce}{September 2019 - August 2023}{Alexandria, VA}
        \startitems
        \item Worked in a student team to overhaul the old organization website, and played a key role in updating and improving website functionality, and website migration to new provider. 
        \item Received promotion to team lead after three years. 
        \item Interviewed, hired, trained a team of student applicants. Led this team in pushing website updates and updating functionality. 
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Service}
    \begin{rSubsection}{Undergraduate CS Consultant}{W\&M CS Department}{September 2022 - Present}{Williamsburg, VA}
        \startitems
        \item Held office hours twice a week for Programming for Data Science (CSCI 140), 	Computational Problem Solving (CSCI 141), and Data Structures (CSCI 241) students during semesters.
        \item Offered advice for debugging code, general guidance for assignments, and helped with conceptual understanding.
        \item Covered Data Structures, Python, and Pandas.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Honors}
    \begin{rSubsection}{Phi Beta Kappa}{W\&M}{November 2023}{Phi Beta Kappa Chapter} \end{rSubsection}

    \begin{rSubsection}{Elias Paparis Scholarship}{W\&M}{March 2023}{W\&M Computer Science Department}
        \startitems
        \item \$2,500 merit-based scholarship awarded to an outstanding CS student with unmet financial need.
    \end{rSubsection}

    \begin{rSubsection}{Robert C. and Muriel M. Jennings Scholarship}{W\&M}{September 2023}{Phi Beta Kappa Chapter} 
        \startitems
        \item \$3,500 merit-based scholarship awarded to an outstanding student with unmet financial need.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Skills}
    {\bf Programming Languages, Frameworks, Tools} 
    \quad Qiskit, Amazon Braket, \LaTeX, Python, C++, JavaScript, SQL, React, Java, C\#, Matlab
    
    {\bf Languages}
    \quad English (native), Chinese (fluent)
\end{rSection}

\end{document}

