\begin{rSection}{Service}

    \begin{rSubsection}{Teaching Assistant} {September 2024 - Present}{}{\small{University of Washington}}
    \begin{itemize}
        \item Modified assignments, assignment autograding on Gradescope, and quizzes.
        \item Graded assignments.
        \item Held twice weekly office hours. 
        \item Fielded student questions on Slack. 
    \end{itemize}
    \end{rSubsection}

    \begin{rSubsection}{Research/Teaching Assistant} {June 2024 - Present}{Advisor: Dr. Chi-Kwong Li}{\small{William \& Mary Math Department}}
        \begin{itemize}
            \item Authoring a set of class notes that serve as a quick introduction to quantum information science from a linear algebra perspective, used for instructing new students in the field.
            \item Collaborated with advisor to refine the content, incorporating feedback to improve the clarity and effectiveness of the instructional materials.
            \item Designed examples and supplementary exercises to reinforce key concepts.
        \end{itemize}
        \end{rSubsection}
    
    \begin{rSubsection}{Intern Mentor} {December 2023 - Present}{-}{\small{Asian Americans in Energy, Environment, and Commerce (AE2C)}}
    \begin{itemize}
        \item Mentoring a high school student intern on the fundamentals of programming and web development.
        \item Provided guidance on project management, direction, and code quality, ensuring the intern's successful completion of several backend projects.
        \item Offered advice for improving algorithm performance and code best practices.  
    \end{itemize}
    \end{rSubsection}
    
    \begin{rSubsection}{Undergraduate Consultant} {August 2022 - May 2024}{Computer Science Consulting}{\small{William \& Mary}}
    \begin{itemize}
        \item Provided assistance to computer science students during the semester by holding office hours twice a week, providing one-on-one support to students. 
        \item Offered advice for debugging code and assignments, covering topics related to data structures and computer science principles.
    \end{itemize}
    \end{rSubsection}
        
\end{rSection}