\begin{rSection}{Professional Experience}

\begin{rSubsection}{Solutions Architect Intern}{2022 - 2023}{Seattle, WA}{\small{Amazon Web Services}}
\begin{itemize}
	\item Implemented an end-to-end quantum error mitigation scheme, replicating a state-of-the-art result. Used Poisson distributions fit on quantum processor metadata to predict and reduce quantum noise. Constructed a quantum circuit transpilation protocol in Python to aid in this endeavor.
	\item Investigated relevant literature in cloud quantum computing, quantum error mitigation, and LLM retrieval augmented generation.
	\item Studied for and achieved the Cloud Practitioner and Associate Solutions Architect AWS Certifications.
	\item Completed mock customer conversations and shadowed customer calls.
\end{itemize}
\end{rSubsection}
\begin{rSubsection}{Junior Software Developer}{2021 - 2022}{McLean, VA}{\small{ESPX Global Inc.}}
\begin{itemize}
	\item Engineered a data lake solution capturing market conditions and features of the electric grid.
	\item Agilely collaborated remotely with a team of developers to create a minimum viable product conforming to client expectations.
	\item Selected, acquired, normalized, and analyzed data using Python, AWS services, and SQL.
	\item Managed and maintained the company website, along with related SSL certificate.
\end{itemize}
\end{rSubsection}
\begin{rSubsection}{Student Intern Team Lead}{2022 - 2023}{Alexandria, VA}{\small{Asian Americans in Energy, Environment, and Commerce}}
\begin{itemize}
	\item Interviewed, hired, trained a team of student applicants as team lead.
	\item Led this team in pushing website updates and updating functionality.
	\item Mentored and developed interns' technical and professional skills.
\end{itemize}
\end{rSubsection}
\end{rSection}
